A Type System for Safe and Scalable Parallelism using Logical Regions

### 2012-07-10 doc/popl2013/intro.tex
More circuit example edits

-- Simulation initialization and invocation
function simulate_circuit[rl,rw,rn] ( all_nodes : node_list<rl,rn>@rl, 
      all_wires : wire_list<rl,rw,rn,rn>@rl, steps : int ), 
      reads(rn,rw,rl), writes(rn,rw,rl) : bool = 
  let pc : <coloring(rn),coloring(rn),coloring(rw)> 
            = color_circuit[rn,rw,rl](all_nodes,all_wires) in
  -- Disjoint partition for the owned nodes of each piece
  partition rn using pc.1 as rn0,rn1 in
  -- Aliased partition for ghost nodes of each piece
  partition rn using pc.2 as rg0,rg1 in
  -- Disjoint partition for the owned wires of each piece
  partition rw using pc.3 as rw0,rw1 in
  let piece0 : CircuitPiece<rl,rw,rn> = 
                build_piece[rl,rw,rn,rw0,rn0,rg0](all_nodes,all_wires,pc.1,pc.2,pc.3,0) in
  let piece1 : CircuitPiece<rl,rw,rn> = 
                build_piece[rl,rw,rn,rw1,rn1,rg1](all_nodes,all_wires,pc.1,pc.2,pc.3,1) in
      execute_time_steps[rl,rw,rn](piece0,piece1,steps)

>>>>

-- Simulation initialization and invocation
function simulate_circuit[rl,rw,rn] ( all_nodes : node_list<rl,rn>@rl, 
                            all_wires : wire_list<rl,rw,rn,rn>@rl, steps : int ), 
      reads(rn,rw,rl), writes(rn,rw,rl) : bool = 
  let pc : <coloring(rn),multicoloring(rn),coloring(rw)> 
            = color_circuit[rn,rw,rl](all_nodes,all_wires) in
  -- Disjoint partition for the owned nodes of each piece
  partition rn using pc.1 as rn0,rn1 in
  -- Aliased partition for ghost nodes of each piece
  partition rn using pc.2 as rg0,rg1 in
  -- Disjoint partition for the owned wires of each piece
  partition rw using pc.3 as rw0,rw1 in
  let piece0 : CircuitPiece<rl,rw,rn> = 
                build_piece[rl,rw,rn,rw0,rn0,rg0](all_nodes,all_wires,pc.1,pc.2,pc.3,0) in
  let piece1 : CircuitPiece<rl,rw,rn> = 
                build_piece[rl,rw,rn,rw1,rn1,rg1](all_nodes,all_wires,pc.1,pc.2,pc.3,1) in
      execute_time_steps[rl,rw,rn](piece0,piece1,steps)
